---
title: "YouTube Statistics Analysis"
author: "Ameerah"
date: "2024-07-04"
output:
  html_document:
    df_print: paged
---

# Introduction

This analysis explores YouTube statistics data sourced from Kaggle. The focus is on understanding patterns across country, channel types, and key metrics such as subscribers, video views, and uploads. The analysis includes descriptive and inferential statistics, as well as bootstrap simulation.

# 1. Load Packages and Dataset

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
library(psych)
library(highcharter)
library(stringr)

# Read CSV
dataset <- read.csv("data/global_youtube_statistics.csv")

# Preview
head(dataset)
```

# 2. Data Cleaning

```{r}
# Clean non-alphanumeric characters
dataset$Youtuber <- str_replace_all(dataset$Youtuber, "[^[:alnum:]\\s]", "")
dataset$Title <- str_replace_all(dataset$Title, "[^[:alnum:]\\s]", "")

# Drop unnecessary columns
dataset <- dataset %>% 
  select(-c(Gross.tertiary.education.enrollment...., Population, Unemployment.rate,
            Urban_population, Latitude, Longitude)) %>%
  drop_na()

# Check missing values
colSums(is.na(dataset))
```

# 3. Exploratory Data Analysis (EDA)

## 3.1 Country and Continent Analysis

```{r}
country_to_continent <- function(country) {
  case_when(
    country %in% c("Afghanistan", "Bangladesh", "India", "Pakistan", "Iraq", "Iran", "Saudi Arabia",
                   "Kuwait", "Jordan", "China", "Indonesia", "Japan", "Malaysia", "Philippines",
                   "Singapore", "Thailand", "Vietnam") ~ "Asia",
    country %in% c("Egypt", "Morocco") ~ "Africa",
    country %in% c("Argentina", "Brazil", "Colombia", "Peru", "Venezuela", "Ecuador") ~ "South America",
    country %in% c("Canada", "United States", "Mexico", "El Salvador", "Cuba") ~ "North America",
    country %in% c("United Kingdom", "France", "Germany", "Italy", "Spain", "Sweden", "Finland",
                   "Switzerland", "Andorra", "Latvia", "Ukraine", "Netherlands", "Russia", "Turkey") ~ "Europe",
    country %in% c("Australia") ~ "Oceania",
    TRUE ~ NA_character_
  )
}

dataset$continent <- factor(sapply(dataset$Country, country_to_continent))

# Frequency table
table(dataset$continent)
```

### Visualization: Top 10 Countries by Views

```{r}
top_country_views <- dataset %>%
  mutate(continent = sapply(Country, country_to_continent)) %>%
  group_by(Country, continent) %>%
  summarise(total_views = sum(video.views), .groups = "drop") %>%
  arrange(desc(total_views)) %>%
  group_by(continent) %>%
  slice_max(total_views, n = 10)

ggplot(top_country_views, aes(x = continent, y = total_views, fill = Country)) +
  geom_bar(stat = "identity") +
  labs(title = "Top 10 Countries by Total Views per Continent",
       x = "Continent", y = "Total Views") +
  theme_minimal() +
  theme(legend.position = "bottom", axis.text.x = element_text(angle = 45))
```

## 3.2 Channel Type

```{r}
dataset$channel_type <- factor(dataset$channel_type)

# Frequency table
table(dataset$channel_type)
```

### Visualization: 3D Column Chart

```{r}
channel_summary <- dataset %>%
  group_by(channel_type) %>%
  summarise(total_views = sum(video.views), .groups = "drop")

highchart() %>%
  hc_chart(type = "column", options3d = list(enabled = TRUE, alpha = 20, beta = 15)) %>%
  hc_xAxis(categories = channel_summary$channel_type) %>%
  hc_add_series(data = channel_summary$total_views, name = "Total Views") %>%
  hc_title(text = "Total Views by Channel Type")
```

## 3.3 Numerical: Subscribers & Video Views

```{r}
describe(dataset$subscribers)
describe(dataset$video.views)
```

### Bubble Chart

```{r}
bubble_data <- dataset %>%
  select(Youtuber, subscribers, video.views, category, Country) %>%
  mutate(
    subscribers = as.numeric(subscribers),
    video.views = as.numeric(video.views)
  )

highchart() %>%
  hc_chart(type = "bubble", zoomType = "xy") %>%
  hc_title(text = "Subscribers vs. Video Views") %>%
  hc_xAxis(
    title = list(text = "Subscribers"),
    labels = list(format = "{value / 1000000}M")
  ) %>%
  hc_yAxis(title = list(text = "Video Views")) %>%
  hc_add_series(
    data = bubble_data,
    type = "bubble",
    hcaes(x = subscribers, y = video.views, z = subscribers, name = Youtuber),
    dataLabels = list(enabled = TRUE, format = '{point.name}'),
    colorByPoint = TRUE,
    name = "Youtuber"
  ) %>%
  hc_tooltip(
    useHTML = TRUE,
    formatter = JS("
      function() {
        var views = this.y;
        if (views >= 1e9) views = (views / 1e9).toFixed(1) + 'B';
        else if (views >= 1e6) views = (views / 1e6).toFixed(1) + 'M';
        else views = views.toFixed(0);

        return '<b>' + this.point.name + '</b><br>' +
               'Subscribers: ' + Highcharts.numberFormat(this.x, 0) + '<br>' +
               'Video Views: ' + views + '<br>' +
               'Country: ' + this.point.Country + '<br>' +
               'Category: ' + this.point.category;
      }
    ")
  )

```

# 4. Inferential Statistics

```{r}
shapiro.test(dataset$subscribers)
shapiro.test(dataset$uploads)

wilcox.test(dataset$uploads, dataset$subscribers, paired = TRUE)
cor.test(dataset$uploads, dataset$subscribers, method = "spearman")
```

# 5. Bootstrap Simulation

```{r}
set.seed(123)

boot_results <- replicate(100, {
  sample_data <- dataset %>% slice_sample(n = nrow(dataset), replace = TRUE)
  model <- lm(subscribers ~ uploads, data = sample_data)
  c(coef(model), summary(model)$r.squared)
})

boot_df <- as.data.frame(t(boot_results))
colnames(boot_df) <- c("intercept", "slope", "r_squared")

summary_stats <- boot_df %>%
  summarise(
    mean_slope = mean(slope),
    sd_slope = sd(slope),
    mean_intercept = mean(intercept),
    sd_intercept = sd(intercept),
    mean_r_squared = mean(r_squared),
    sd_r_squared = sd(r_squared)
  )

summary_stats

